Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-29 paper.tex
Check Vivechna suggegstions

\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures. \notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;  
    Probably "Analytical model for  porous silicon structures with 1D gradient refractive index"}} }
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\begin{document}

\maketitle

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{Surfaces with  the gradient in the refractive index have 
attracted attention due to their capacity to unpair the relation 
between the shape of the optical 
lens with its optical response.  For enhancing the versatility  of 
electrochemical gradients and its possible usage in 
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial predictability of 
porosity and the corresponding etching rate.  In this work, we propose a 
simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with 
lateral porosity and thickness gradient (produced using pin Pt electrode) 
with scanning electron microscopy andultraviolet-visible-near infrared 
reflectance spectroscopy was found to be in conformity with the properties 
predicted through the proposed model. In addition, 
as the results allow us to obtain the complete dependence of porosity,
dielectric function and the corresponding etching rate for each current
density from some measurements performed on a single or a couple of samples,
the proposed model can facilitate the designing of novel sensing devices 
based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

@@

Gradient in the refractive index (GRIN) of a material is of 
importance not only due to the possibility of being able to 
engineer/tune the propagation of light within the structure for 
applications such as flat lenses, but also for several 
interesting biological applications where the continual topographical 
variation is being exploited \cite{pierscionek2012gradient}. As an example, 
roughness dependent  response of the cells has been tested on such 
materials for applications in medical implants \cite{bai2020bioinspired}.  
 Gradients have also been employed for several 
technological applications such as high-yield screening of catalysts, 
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction, 
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew. 
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227], 
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS 
on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.  
Among the electrochemical methods, compositional and doping density changes 
in the conducting polymer have been used to produce the gradients using Indium tin 
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].   
Electrochemically induced potential gradients have been shown to catalyze the 
reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer 
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical, 
fast and easy approach with an additional advantage of being compatible 
with VLSI devices and integrable with microelectronics, for the fabrication 
of refractive index (pore size) gradient has been the development of asymmetric 
electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.  
Although porous silicon initially stimulated the interest of the scientific 
community due to visible PL at room temperature, presently it has 
been accepted as a multifaceted optical material due to its large surface 
area, biocompatibility, ease of fabrication and tunable refractive index. 
Porous silicon emanating applications now cover various fields such as 
chemical and biosensor \cite{kumar2020porous},
%[Porous Silicon Fabry–Pérot Interferometer for
%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
%10.1021/acssensors.0c00348], 
microelectronics and MEMS \cite{martinez2016dual},as well as a 
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically, 
the temporal variation of current density results in the variation of 
porosity along the depth for the easy fabrication of different kinds 
\cite{perez2018reflectivity} of 1D photonics crystals. 
Although the conventional fabrication of PS requires laterally 
homogeneous samples (with same structural characteristics on the 
porous surface), asymmetric configuration to produce porous silicon 
with a lateral gradient (in terms of optical thickness/ pore size and thickness 
of the porous layer) has also been exploited for different applications 
\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)  
is positioned perpendicular  to the surface of the Si substrate (anode) 
at one end or the center  of the cell, resulting  in a decrease in current 
density  with an increase in the distance from the electrode
 \cite{khung2008using, clements2011mesenchymal}. 
The resulting porous surface can have pore sizes ranging from a few nanometers  
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and 
the corresponding  thickness obtained on the same chip can be controlled by 
adjusting the location of the pin/circular electrode,  anodizing current density
and etching time period for a given silicon wafer.   Sailor Group 
in 2002 \cite{collins2002determining, sailor2012porous} applied it 
for the determination of protein size. 
Additionally, due to the biocompatible nature of PS, possible gating of 
the optical response by variation in pH of the solution was shown to 
trap/release the biomolecule for possible drug delivery applications. 
Similar asymmetric electrode configuration was used to fabricate 
optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
% [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
% "Painting a rainbow on silicon–a simple method to 
% generate a porous silicon band filter gradient.
% " physica status solidi (a) 202.8 (2005): 1616-1618.] 
for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}. 
Additionally it has been shown that the combination of thermal  oxidation  and 
infiltration of TiO2  by ALD offers the  opportunity to manufacture 
a high refractive indices contrast in visibly transparent GRIN 
optical elements from PS \cite{ocier2017tunable}.    
Krueger et al. \cite{krueger2018electrochemical} in 2018 used porous 
silicon 1D GRIN structure 
infiltrated with polymer to synthesize flat microns arrays. 
%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]

@@

\section{Theory: current density}
\label{sec:theory}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the etching rate and the thickness of the
porous layer. Nevertheless, it is not a simple task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be numerically calculated for any
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

Poisson's equation within an orthothombic lattice of size

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a brass \notaC{ laton. gold plate} 
\notaL{Lo inventé; de qué material es
  el contacto bajo la muestra?} which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of GRIN  PS Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through electrochemical
anodization of a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
\notaC{room temperature, no controle latempertaura}
,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
  todo esto sí corresponda a tus últimas muestras} \notaC{SI corresponde}
   After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
of about $3\,\text{cm}^2$. The height of the liquid was set at
$c=1\,\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\,\text{mm}$ insulated by a
teflon cylinder of external diameter $\,2\text{mm}$, with an uncovered
tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
$I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.

>>>>

\title{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina de la Cruz}
\author[2]{V. Agarwal}
\author[3]{W. L. Mochán}

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\affil[3]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\begin{document}

\maketitle
\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
  Probably "Analytical model for  porous silicon structures with 1D
  gradient refractive index)}
\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
\begin{abstract}
  We propose a simple setup with which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response.
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial
predictability of porosity and the corresponding etching rate.
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with
lateral porosity and thickness gradient (produced using pin Pt electrode)
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was
found to be in conformity with the properties predicted through
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each
current density from some measurements performed on a single or
a couple of samples, the proposed model can facilitate the designing
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

@@

Surfaces with gradient in the refractive index (GRIN) are of
importance not only due to the possibility of being able to
engineer/tune the propagation of light within the structure’s
surface for applications such as flat lenses, but also for several
interesting biological applications where the continual topographical
variation is being exploited \cite{pierscionek2012gradient}. As an example,
roughness dependent  response of the cells has been tested on such
materials for applications in medical implants \cite{bai2020bioinspired}.
 Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew.
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman,
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas.
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS
on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.
Among the electrochemical methods, compositional and doping density changes
in the conducting polymer have been used to produce the gradients using Indium tin
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach with an additional advantage of being compatible
with VLSI devices and integrable with microelectronics, for the fabrication
of refractive index (pore size) gradient has been the development of asymmetric
electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.

Although porous silicon initially stimulated the interest of the scientific
community due to visible PL at room temperature, presently it has
been accepted as a multifaceted optical material due to its large surface
area, biocompatibility, ease of fabrication and tunable refractive index.
Porous silicon emanating applications now cover various fields such as
chemical and biosensor \cite{kumar2020porous},
%[Porous Silicon Fabry–Pérot Interferometer for
%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar,
%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI:
%10.1021/acssensors.0c00348],
microelectronics and MEMS \cite{martinez2016dual},as well as a
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically,
the temporal variation of current density results in the variation of
porosity along the depth for the easy fabrication of different kinds
\cite{perez2018reflectivity} of 1D photonics crystals.
Although the conventional fabrication of PS requires laterally
homogeneous samples (with same structural characteristics on the
porous surface), asymmetric configuration to produce porous silicon
with a lateral gradient (in terms of optical thickness/ pore size and thickness
of the porous layer) has also been exploited for different applications
\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)
is positioned perpendicular  to the surface of the Si substrate (anode)
at one end or the center  of the cell, resulting  in a decrease in current
density  with an increase in the distance from the electrode
 \cite{khung2008using, clements2011mesenchymal}.
The resulting porous surface can have pore sizes ranging from a few nanometers
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
the corresponding  thickness obtained on the same chip can be controlled by
adjusting the location of the pin/circular electrode,  anodizing current density
and etching time period for a given silicon wafer.   Sailor Group
in 2002 \cite{collins2002determining, sailor2012porous} applied it
for the determination of protein size.
Additionally, due to the biocompatible nature of PS, possible gating of
the optical response by variation in pH of the solution was shown to
trap/release the biomolecule for possible drug delivery applications.
 Similar asymmetric electrode configuration was used to fabricate
 optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
% [Li, Yang Yang, Peter Kim, and Michael J. Sailor.
% "Painting a rainbow on silicon–a simple method to
% generate a porous silicon band filter gradient.
% " physica status solidi (a) 202.8 (2005): 1616-1618.]
for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}.
 Additionally it has been shown that the combination of thermal  oxidation  and
 infiltration of TiO2  by ALD offers the  opportunity to manufacture
a high refractive indices contrast in visibly transparent GRIN
optical elements from PS \cite{ocier2017tunable}.
Kruger et al showed the \cite{krueger2016porous}
%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient
%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]
In addition the same group \cite{krueger2018electrochemical} used porous silicon 1D GRIN structure infiltrated with polymer to synthesize flat microns arrays.

@@

\section{Theory: current density}
\label{sec:theory}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the etching rate and the thickness of the
porous layer. Nevertheless, it is challeging to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be numerically calculated for any
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

Poisson's equation within an orthorhombic lattice of size

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a brass \notaC{ laton. gold plate}\notaL{Porqué
  vivechna dice silver/copper?}
\notaL{Lo inventé; de qué material es
  el contacto bajo la muestra?} which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
Single layer PS structures were fabricated through electrochemical
anodization of (100) oriented $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
\notaC{room temperature, no controle latempertaura}
,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
  todo esto sí corresponda a tus últimas muestras} \notaC{SI corresponde}
   After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
of about $3\,\text{cm}^2$. The height of the liquid was set at
$c=1\,\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\,\text{mm}$ insulated with
teflon tape \notaL{Según Vivechna esto es falso: by a
teflon cylinder of external diameter $\,2\text{mm}$}, with an uncovered
tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
$I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.
